### 2011-12-03 AffineLieAlgebras/Thesis/3.tex
Translations in chapter 3.

To study relations between injection fan technique and splint let us 
consider the case when one of the stems $\Delta _{1}=\Delta _{\af}$ 
is a root subsystem.

Splint $\Delta \approx (\Delta _{1},\Delta _{2})$ is called ''injective'' if
$\Delta _{1}=\Delta _{\af}$, is a root subsystem
in $\Delta $ corresponding to a regular reductive subalgebra $\af%
\hookrightarrow \gf$.

In case of injective splint the second stem $\Delta _{\frak{s}}:=\Delta
_{2}=\Delta \setminus \Delta _{\af}$ can be translated into a product (%
\ref{product}) and it defines an injection fan $\Gamma _{\af%
\hookrightarrow \gf}$. Denote by $\Delta_{\mathfrak{s}0}$ the coimage of the second embedding $\phi:\Delta_{\mathfrak{s}0}\to \Delta_{\gf}$.
The following conjecture follows.

\begin{Cnj}
Each injective splint $\Delta \approx (\Delta _{\af},\Delta _{\frak{s}})
$ defines an injection fan with the carrier $\left\{ \xi \right\} _{\af%
\rightarrow \gf}$ fixed by the product
\begin{equation}
\prod_{\beta \in \Delta _{\frak{s}}^{+}}\left( 1-e^{-\beta }\right)
=-\sum_{\gamma \in P}s(\gamma )e^{-\gamma }\quad   \label{splint product}
\end{equation}
\end{Cnj}

In case of injective splint we say that subalgebra $\af\hookrightarrow \gf$
splinters $\Delta $ (and call $\af$ the ''splinting subalgebra'' of $%
\gf$). In \cite{richter2008splints} splints are classified (see Appendix there)
and the first three types of them are injective.

\section{How stems define multiplicity functions}

@@

In this Section we study properties of injective splints  $\Delta \approx (\Delta _{\af},\Delta _{\frak{s}})
$. It will
be demonstrated that in this case to find branching
coefficients for a splinting injection $\af\hookrightarrow
\gf$ means to find weight multiplicities of an irreducible
$\frak{s}$-module $L_{\frak{s}}^{\nu }$ with fixed highest weight
$\nu $. Notice that $\frak{s}$ must not be a subalgebra of
$\gf$.

>>>>

Чтобы показать связь веера вложения со сплинтом рассмотрим случай, когда один из стеблей $\Delta _{1}=\Delta _{\af}$  является подсистемой корневой системы.

Сплинт $\Delta \approx (\Delta _{1},\Delta _{2})$ называется ``инъективным'', если $\Delta _{1}=\Delta _{\af}$, -- подсистема корневой системы $\Delta $, соответствующая регулярной редуктивной подалгебре $\af\hookrightarrow \gf$.

В случае инъективного сплинта второй стебель $\Delta _{\frak{s}}:=\Delta_{2}=\Delta \setminus \Delta _{\af}$ может быть переписан как произведение (\ref{product}) и определяет веер вложения  $\Gamma _{\af\hookrightarrow \gf}$. Обозначим через $\Delta_{\mathfrak{s}0}$ кообраз второго вложения $\phi:\Delta_{\mathfrak{s}0}\to \Delta_{\gf}$. Верна следующая гипотеза.

\begin{Cnj}
Каждый инъективный сплинт $\Delta \approx (\Delta _{\af},\Delta _{\frak{s}})$ определяет веер вложения с носителем $\left\{ \xi \right\} _{\af\rightarrow \gf}$, задающимся произведением
\begin{equation}
\prod_{\beta \in \Delta _{\frak{s}}^{+}}\left( 1-e^{-\beta }\right)
=-\sum_{\gamma \in P}s(\gamma )e^{-\gamma }\quad   \label{splint product}
\end{equation}
\end{Cnj}

В случае инъективного сплинты мы можем сказать, что подалгебра $\af\hookrightarrow \gf$ расщепляется $\Delta$ (и назовем $\af$ ``расщепляющей подалгеброй'' алгебры $\gf$).  Сплинты были классифицированы в работе \cite{richter2008splints}  (см. Приложение в работе) и первые три класса сплинтов в этой классификации инъективны.

\section{Как стебли определяют функции кратности}

@@

В этом разделе мы рассмотрим свойства инъективных сплинтов $\Delta \approx (\Delta _{\af},\Delta _{\frak{s}})$. Мы покажем, что в этом случае вычисление коэффициентов ветвления для расщепляющего вложения $\af\hookrightarrow\gf$ эквивалентно нахождению кратностей весов неприводимого $\frak{s}$-модуля $L_{\frak{s}}^{\nu }$ с определенным старшим весом $\nu $. Заметим, что алгебра $\frak{s}$ не обязательно должна быть подалгеброй $\gf$.
